Macro Impacts

### 2016-08-07 Macro Impacts Revised.tex
Python Functional but SLOW
Finished Matlab - Python works but needs speeding up
Based on some tests, i’d guess that the detectable energy density
threshold should be about 10^6 J/km^2 = 1J/m^2. That sounds reasonable,
but how do we show it?
Displacement
Wrong, but the process is there.

Note, the bigger $r_0$ and $\Delta r$ are, the bigger $E_{\te{attenuated}}$ will be. A very generous over estimate is to say that $\Delta r = r_0 = 1\te{m}$. Another way to do this is as we did earlier, by starting the propagation once the wave has reached a certain pressure $\bar p \approx 10^8\te{Pa}$.

@@

\epsilon \geq 6\times 10^{-9} \te{J\,km}^{-2}\,.

>>>>

Note, the bigger $r_0$ and $\Delta r$ are, the bigger $E_{\te{attenuated}}$ will be. A very generous over estimate is to say that $\Delta r = r_0 = 1\te{m}$. Another way to do this is as we did earlier, by starting the propagation once the wave has reached a certain pressure $\bar p \approx 10^8\te{Pa}$. Then
 r_0 = \f{K^2}{\lambda+2\mu} \f{3}{2\pi\Delta r}\f{\rho\sigma_Xv_X^2 }{p_0^2}-\f{3}{4}\Delta r
A quick plot shows that the attenuation here is pretty much negligible.

@@

\epsilon \geq 6\times 10^{-15} \te{J\,m}^{-2}\,.
This is probably wrong. They can measure a displacement of $3\times 10^{-10}\te{m}$. We can calculate the displacement due to a seismic $p$-wave. Suppose $P$ is the Fourier transform of the pressure wave. Then the displacement field's Fourier transform is 
U(\vec k) =\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,. 
The displacement is then... I FORGOT AN $\omega t$!!! I'll redo later tonight
u &= \int\f{\diff^3 k}{(2\pi)^3}\I\f{P(\vec k)}{K}\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x - \I\omega t}\,,\\
&=\f{1}{K}\int\f{\diff^3 k}{(2\pi)^3}\I\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))\f{\vec k}{k^2}e^{\I \vec k\cdot\vec x}\,,\\
&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\f{k^2\sin\theta}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\f{\hat k}{k}e^{\I (kx\cos\varphi)}\,,\\
&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff k\diff\theta\diff\phi}{(2\pi)^2}\tan\theta\sin\p{\f{h k\cos\theta}{2}}\hat k e^{\I (kx\cos\varphi)}\,,\\
&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta\diff\phi}{(2\pi)^2}\ps{\f{2h\cos\theta-2e^{\I k_0 x\cos\varphi}\p{h\cos\theta\cos\p{\f{h}{2}k_0\cos\theta} - 2\I x\cos\varphi\sin\p{\f{h}{2}k_0\cos\theta}}}{h^2\cos^2\theta-4x^2\cos^2\varphi}}\,,\\
&=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{2h-2e^{\I k_0 x\cos\theta}\p{h\cos\p{\f{h}{2}k_0\cos\theta} - 2\I x\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,.
By proper choice of coordinates, we can insist that $\varphi = \theta$. Moreover, we know that $u$ is real, and hence we can write
u &=\I2 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{-2\I\p{h\sin\p{k_0 x\cos\theta}\cos\p{\f{h}{2}k_0\cos\theta} - 2 x\cos\p{k_0 x\cos\theta}\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,,\\
&=4 p_0\f{(b^2f_1(b)-a^2f_1(a))}{K}\int\f{\diff\theta}{2\pi}\ps{\f{\p{h\sin\p{k_0 x\cos\theta}\cos\p{\f{h}{2}k_0\cos\theta} - 2 x\cos\p{k_0 x\cos\theta}\sin\p{\f{h}{2}k_0\cos\theta}}}{(h^2-4x^2)\cos\theta}}\,,\\
&=k_0\f{p_0}{2}\f{(b^2f_1(b)-a^2f_1(a))}{K}\p{_p\te{F}_q\ps{\pc{\f12},\pc{1,\f32},-\p{\f{k_0(h+2x)}{4}}^2} -_p\te{F}_q\ps{\pc{\f12},\pc{1,\f32},-\p{\f{k_0(h-2x)}{4}}^2}}
